|

### 2022-09-16 article/article.Rmd
commit final touches paper

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.

>>>>

[^umberto]: Assistant Teaching Professor, Department of Political Science and Computational Social Sciences Program, University of California, San Diego, <umbertomig@ucsd.edu>, <http://umbertomig.com>. Corresponding author.

### 2022-09-16 article/article.tex
commit final touches paper

% Author
\author{Danilo Freire\footnote{Senior Lecturer, School of Social and
  Political Sciences, University of Lincoln,
  \href{mailto:dfeire@lincoln.ac.uk}{\nolinkurl{dfeire@lincoln.ac.uk}},
  \url{https://danilofreire.github.io}.} \and Umberto
Mignozzetti\footnote{Visiting Assistant Professor, Quantitative Theory
  and Methods Department, Emory University,
  \href{mailto:umberto.mignozzetti@emory.edu}{\nolinkurl{umberto.mignozzetti@emory.edu}},
  \url{http://umbertomig.com}. Corresponding author.} \and Catarina
Roman\footnote{PhD Student, University of California, San Diego,
  \href{mailto:acroman@ucsd.edu}{\nolinkurl{acroman@ucsd.edu}},
  \url{http://catarinaroman.github.io}.} \and Huzeyfe
Alptekin\footnote{Independent Researcher,
  \href{mailto:huzeyfealptekin@gmail.com}{\nolinkurl{huzeyfealptekin@gmail.com}}.}}

>>>>

% Author
\author{Danilo Freire\footnote{Senior Lecturer, School of Social and
  Political Sciences, University of Lincoln,
  \href{mailto:dfeire@lincoln.ac.uk}{\nolinkurl{dfeire@lincoln.ac.uk}},
  \url{https://danilofreire.github.io}.} \and Umberto
Mignozzetti\footnote{Assistant Teaching Professor, Department of
  Political Science and Computational Social Sciences Program,
  University of California, San Diego,
  \href{mailto:umbertomig@ucsd.edu}{\nolinkurl{umbertomig@ucsd.edu}},
  \url{http://umbertomig.com}. Corresponding author.} \and Catarina
Roman\footnote{PhD Student, University of California, San Diego,
  \href{mailto:acroman@ucsd.edu}{\nolinkurl{acroman@ucsd.edu}},
  \url{http://catarinaroman.github.io}.} \and Huzeyfe
Alptekin\footnote{Independent Researcher,
  \href{mailto:huzeyfealptekin@gmail.com}{\nolinkurl{huzeyfealptekin@gmail.com}}.}}
